Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-12-27 paper/lncsFormat.tex
remove pagenum for camera-ready
update acknowledgements

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\titlerunning{\ }
\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}

\maketitle

@@

\section*{Acknowledgments}\label{sec:Acknowledgments}
This research is supported by the Natural Science Foundation of China (Grant No. 61300003, 61572043), and the Specialized Research Fund for the Doctoral Program of Higher Education (Grant No. 20130001120001).

%\newpage
\bibliographystyle{unsrt}
\small
\bibliography{paperbib}

>>>>

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\titlerunning{Transfer Learning for Accurate Event Detection\ }
\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}

\maketitle
% BEGIN
% To Proceeding Editors:
% Special codes there for remove page numbers in the LaTeX documents
\thispagestyle{empty}
\pagestyle{empty}
%
% END

@@

\setlength{\parindent}{0pt}\textbf{Acknowledgments.} This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).
%\newpage
\bibliographystyle{unsrt}
\small
\bibliography{paperbib}
